### 2013-05-04 paper/tex/design.tex

\section{Framework Design}\label{sec:design}
\subsection{The Problem-Solution Abstraction}
Many different types of hard problem we encounter have various input structure. For instance, 3-SAT problem input a logic expression while Clique problem needs a graph structure. Those different types of inputs brings the challenges to the CloudCache framework, because it is possible the CloudCache framework host many different types of problems and solutions and the cache query operation need to find the exact solutions for a certain problem. If we do not have a uniform structure for the all problems, the complexity in localizing problems and its solutions will be very large.

@@

\subsection{Core System Design}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{pics/workflow.pdf}
\caption{The Logic Diagram of CloudCache}
\label{fig:logic}
\end{figure}

The CloudCache framework (Fig.~\ref{fig:logic}) includes four types of nodes and three computation phases in the cloud infrastructure. The nodes are \emph{Master Node}, \emph{Slave Node}, \emph{Data Node} and \emph{Sink Node}; the three phases are \emph{Job Distribution Phase}, \emph{Task Solve Phase} and \emph{Solution Sink Phase}. In addition, the \emph{Client Problem} exists outside of the cloud infrastructure which needs to be submitted into the CloudCache framework.

@@

Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node, selected by the same hash function. We use a hash function to shard the queries because we consider the load balance of the Data Node which is much busier than Slave Node or Master Node in the system. In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job. Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the load at the Sink Node is significant which defects the whole system's throughput. Therefore, we have a small optimization that buffers the solution in each Slave Node until certain amount, then the Slave Node will report the buffered results together at once.

\subsection{Framework Generalness}
An expected design goal of CloudCache is the generalness, we want to make this framework to be a proper and simple approach to solve many different types of hard problems in the cloud. According to the design, only two things need to be defined by the developer before using the framework. First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself. After finishing the two parts, the developer can submit a batch of problem as a job to the Master Node, where each problem is regarded as a task. Then the framework will start executing the batch job. In this section, we will show two hard problems' solution using CloudCache framework.

\subsubsection{3-SAT Problem}
The 3-SAT problem has an input of an boolean expression which contains many boolean variables' combinations in 3-conjunctive-normal-form clauses. For example, Eq.~\ref{eq:3-sat} shows an example 3-SAT problem which has $5$ boolean variables and has three clauses. For this problem, we use the expression vector as the key, but the vector is in a specific format. The boolean variable's index represents the variable itself in the vector, and the the index is set to be negative is the boolean variable has a ``not'' operator. The elements in expression are separated by a comma. Therefore, the \emph{key} for Eq.~\ref{eq:3-sat} is $[1,2,-3,2,3,4,3,-4,5]$.

@@

The kernel-solver has two stages, the first stage is to check if the expression or any subexpression has been solved. We use a linear scan to do it by moving the head clause and check the subexpression between the head clause and the end one. For the example in Eq.~\ref{eq:3-sat}, we will check Eq.~\ref{eq:3-sat1},~\ref{eq:3-sat2},~\ref{eq:3-sat3}. If any of the subexpression has been solved, we will retrieve its solution then validate if the assignment can satisfy the whole expression. If so, we do not need a brute-force method to solve it again but just return the assignment in the cache. Otherwise, the brute-force method has to be run and we need to store the solved assignment in the cache. The two simple APIs to query and store key/value in the CloudCache make the operations very easy to do.

@@

Similarly, we first need to abstract the problem-solution pairs. For the problem, we use a matrix $\mathbf{R}_{n\times n}$ to represent the graph which is the \emph{key}, and the \emph{value} is the color assignment vector $\mathbf{a} = [a_1, a_2, ..., a_n]$ where $n$ is the number of vertex in the graph.

The kernel-solver is also using a linear scan to all the vertices. For each vertex, we remove the edges connected to the vertex, then we have a new adjacent matrix $\hat{\mathbf{R}}_{(n-1)\times (n-1)}$ which is actually a subgraph of the original one. For this subgraph, we query the CloudCache to retrieve the existing color assignment. If success, we need to validate the assignment by enumerating the color of the removed vertex combining with the existing solution to see if the complete assignment can fit into the original graph. If so, we can cache the solution; if not, we continue removing another vertex in $\mathbf{R}_{n\times n}$ until we scan all the vertices one time. If cache is not working at all, the brute-force solver is triggered.

>>>>

\section{Framework Design}\label{sec:design}
\subsection{The Problem-Solution Abstraction}
Many different types of hard problem we encounter have various input structures. For instance, 3-SAT problem inputs a logic expression while Clique problem needs a graph structure. Those different types of inputs bring the challenge to the CloudCache framework, because it is possible the CloudCache framework hosts many different types of problems and solutions and the cache query operations need to find the exact solutions for a certain problem. If we do not have a uniform structure for all problems, the complexity in localizing problems and its solutions will be very large.

@@

\subsection{Core System Design}
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{pics/workflow.pdf}
\caption{The Logic Diagram of CloudCache}
\label{fig:logic}
\end{figure}

The CloudCache framework (Fig.~\ref{fig:logic}) includes four types of nodes and three computation phases in the cloud infrastructure. The nodes are \emph{Master Node}, \emph{Slave Node}, \emph{Data Node} and \emph{Sinker Node}; the three phases are \emph{Job Distribution Phase}, \emph{Task Solve Phase} and \emph{Solution Sink Phase}. In addition, the \emph{Client Problem} exists outside of the cloud infrastructure which needs to be submitted into the CloudCache framework.

@@

Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node selected by the same hash function. We use a hash function to shard the queries because we consider the load balance of the Data Node, which is much busier than Slave Node or Master Node in the system. In addition to cache the problem's solution, the solution needs to report to the Sinker Node where the client program will come and retrieve the final results for all tasks in the job after the system finishes the job. Note that we only have single Sinker Node while the each kernel-solver will report its results to the Sinker Node, the load at the Sinker Node is significant which defects the whole system's throughput. Therefore, we have a small optimization that buffers the solution in each Slave Node until certain amount, then the Slave Node will report the buffered results together at once.

\subsection{Framework Generalness}
An expected design goal of CloudCache is the generalness, we want to make this framework to be a proper and simple approach to solve many different types of hard problems in the cloud. According to the design, only two things need to be defined by the developer before using the framework. First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself. After finishing the two parts, the developer can submit a batch of problems as a job to the Master Node, where each problem is regarded as a task. Then the framework will start executing the batch job. In this section, we will show two hard problems' solutions using CloudCache framework.

\subsubsection{3-SAT Problem}
The 3-SAT problem has an input of an boolean expression which contains many boolean variables' combinations in 3-conjunctive-normal-form clauses. For example, Eq.~\ref{eq:3-sat} shows an example 3-SAT problem which has $5$ boolean variables and has three clauses. For this problem, we use the expression vector as the key, but the vector is in a specific format. The boolean variable's index represents the variable itself in the vector, and the the index is set to be negative if the boolean variable has a ``not'' operator. Therefore, the \emph{key} for Eq.~\ref{eq:3-sat} is $[1,2,-3,2,3,4,3,-4,5]$.

@@

The kernel-solver has two stages, the first stage is to check if the expression or any subexpression has been solved. We use a linear scan to do it by traversing from the head clause and check the subexpression between the head clause and the end one. For the example in Eq.~\ref{eq:3-sat}, we will check Eq.~\ref{eq:3-sat1},~\ref{eq:3-sat2},~\ref{eq:3-sat3}. If any of the subexpression has been solved, we will retrieve its solution then validate if the assignment can satisfy the whole expression. If so, we do not need a brute-force method to solve it again but just return the assignment in the cache. Otherwise, the brute-force method has to be run and we need to store the solved assignment in the cache. The two simple APIs to query and store key/value in the CloudCache make the operations very easy to do.

@@

Similarly, we first need to abstract the problem-solution pairs. For this problem, we use a matrix $\mathbf{R}_{n\times n}$ to represent the graph which is the \emph{key}, and the \emph{value} is the color assignment vector $\mathbf{a} = [a_1, a_2, ..., a_n]$ where $n$ is the number of vertex in the graph.

The kernel-solver also uses a linear scan to all the vertices. For each vertex, we remove the edges connected to the vertex, then we have a new adjacent matrix $\hat{\mathbf{R}}_{(n-1)\times (n-1)}$ which is actually a subgraph of the original one. For this subgraph, we query the CloudCache to retrieve the existing color assignment. If success, we need to validate the assignment by enumerating the color of the removed vertex and combining with the existing solution to see if the complete assignment can fit into the original graph. If so, we can cache the solution; if not, we continue removing another vertex in $\mathbf{R}_{n\times n}$ until we scan all the vertices. If cache is not working at all, the brute-force solver otherwise is triggered.

### 2013-05-04 paper/tex/implementation.tex

\subsection{The CloudCache Infrastructure}
As is shown in Fig.~\ref{fig:system}, the infrastructure in the cloud consists of four different types of nodes: Master Node, Slave Node, Data Node and Sink Node. Outside of the cloud infrastructure, we have a Client which will submit the job to the Master Node. After the job is done, the Sink Node will push the job results to the Client.

The Master Node runs a multi-threaded TCP server, waiting for the job submitted from the Client. We consider the possibility of concurrent job submission from the clients, then the multi-threaded server is required. However, we do not optimize the server's performance under some pressure test. The Slave Node is also a multi-threaded TCP server, but once the Slave Node receives the job distributed from the Master Node, it will fork a worker thread to execute every task in the job. We do not fork multiple threads for each task because we do not want the first arrive job's tasks overwhelm the Slave Node (it is possible for Slave Node to run different jobs concurrently).

@@

Finally, the Sink Node is the one to collect all the results and provide the final job result to the Client. To avoid the Slave Node's highly frequent task report, we buffer the report at the Slave Node until the buffer is full. This small optimization reduce the load of Sink Node, and increase the Slave Node's efficiency as well (task reporting blocks the Slave Node moving forward).

@@

\subsection{Software Architecture}
We use Python as the language to implement the system. It consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.

@@

\item slave.py. This module is the component to start a Slave Node. It includes a multi-threaded TCP server as well, and a job execution handler and some statistic variables.
\item sink.py. The Sink Node module which receives the accumulated task report and dump the solutions to disk. After the job finished, the Client can come to retrieve the results.
\item kernel.py. The core module to kernel-solver. A developer should define a class to solve the problem, then the Slave Node will call the kernel-solver based on the configuration.
\item tools.py. It defines many helper class to help simplify the architecture like JobDispatcher, etc.
\item configure.py. The place is used to define any global configuration details, for instance, the Master Node, Slave Node, Data Node and Sink Node.
\end{itemize}

@@

\subsection{Programming Interface}
Two important programming interface in the CloudCache is in the tools.py module. The two APIs are \emph{tools.PersistentStorageManager.query(key)} and \emph{tools.PersistentStorageManager.push(key, value)}.

@@

\subsection{Implementation Optimizations}
After we implement the first version, we do not find too much advantages of the CloudCache framework. Thereafter, we analyze the code we write, and we realize the interaction between the Slave Node and Data Node are too frequent during the problem solving phase, which is reaching the benchmark upper bound of the Data Node. Each query and push operations costs more time than it should be. Therefore, we use a pipeline technique to solve the problem. Every time the problem is fully solved, either through cache query or brute-force, we put the result key-value pair into a pipeline. When the pipeline has certain number of solutions need to be cached in the cloud, we execute the whole pipeline once. This brings a decent performance gain for the CloudCache framework.

>>>>

\subsection{The CloudCache Infrastructure}
As is shown in Fig.~\ref{fig:system}, the infrastructure in the cloud consists of four different types of nodes: Master Node, Slave Node, Data Node and Sinker Node. Outside of the cloud infrastructure, we have a Client which will submit the job to the Master Node. After the job is done, the Sinker Node will push the job results to the Client.

The Master Node runs a multi-threaded TCP server, waiting for the job submitted from the Client. We consider the possibility of concurrent job submission from the clients, then the multi-threaded server is required. However, we do not optimize the server's performance under some pressure test. The Slave Node is also a multi-threaded TCP server, but once the Slave Node receives the job distributed from the Master Node, it will fork a worker thread to execute every task in the job. We do not fork multiple threads for multiple tasks because we do not want the first arrive job's tasks overwhelm the Slave Node.

@@

Finally, the Sinker Node is the one to collect all the results and provide the final job result to the Client. To avoid the Slave Node's highly frequent task report, we buffer the report at the Slave Node until the buffer is full. This small optimization reduce the load of Sinker Node, and increase the Slave Node's efficiency as well (task reporting blocks the Slave Node moving forward).

@@

\subsection{Software Architecture}
We use Python to implement the system. The software stack consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.

@@

\item slave.py. This module is the component to start a Slave Node. It includes a multi-threaded TCP server as well, and a job execution handler and some statistic variables.
\item sinker.py. The Sinker Node module which receives the accumulated task report and dumps the solutions to disk. After the job finished, the Client can come to retrieve the results.
\item kernel.py. The core module to kernel-solver. A developer should define a class to solve the problem, then the Slave Node will call the kernel-solver based on the configuration.
\item tools.py. It defines many helper class to help simplify the architecture like JobDispatcher, etc.
\item configure.py. The place is used to define any global configuration details, for instance, the Master Node, Slave Node, Data Node and Sinker Node.
\end{itemize}

@@

\subsection{Programming Interface}
Two important programming interfaces in the CloudCache is in the tools.py module. The two APIs are \emph{tools.PersistentStorageManager.query(key)} and \emph{tools.PersistentStorageManager.push(key, value)}.

@@

\subsection{Implementation Optimizations}
After we implement the first version, we do not find too much advantages of the CloudCache framework. Thereafter, we analyze the code we write, and we realize the interaction between the Slave Node and Data Node are too frequent during the problem solving phase, which is reaching the benchmark upper bound of the Data Node. Each query or push operation costs more time than it should be. Therefore, we use a pipeline technique to solve the problem. Every time the problem is fully solved, either through cache query or brute-force, we put the result key-value pair into a pipeline. When the pipeline has certain number of solutions need to be cached in the cloud, we execute the whole pipeline once. This brings a decent performance gain for the CloudCache framework.

### 2013-05-04 paper/tex/introduction.tex

By the booming time of cloud computing, people may have the chance to rethink of the way to solve some existing hard problems in computer science. The hard problems (usually belongs to the NP-Complete category like 3-SAT) often require exponential computation time to traverse the solution space in a brute-force manner. In addition, people may need to solve the same types of problems again and again in different instance. Some instances or subproblems possibly have been solved by others. Therefore, we come to the idea that \emph{cache the existing solutions to those problems and query the solutions before we solve any other problems}.

One immediate challenge of this idea is the storage requirement. Even the same type of problem, e.g. 3-SAT, could have numerous problem instance, which may require several disks to store them, let alone we have many different types of hard problems. Cloud computing, at this point, could be a proper plagiarism because it is much less expensive to build a large scale storage and its management system. The other challenge is how we abstract the hard problems in a way that the platform we build could be more general to many different type of hard problems.

In this document, we propose \emph{CloudCache} framework which is built on top of general cloud computing platform and provides the interface to query, cache and solve hard problems in an easier way. The CloudCache framework abstracts the \emph{problem-solution} pair into \emph{key-value} objects, and uses some object storage system to cache existing problems and solutions. Further, the CloudCache framework provides a general problem solving interface \emph{kernel-solver}, so that the developer can easily write a problem's solution and solve it within the CloudCache's framework. CloudCache executes kernel-solver in a distributed way which tries to maximize the framework's problem solving throughput.

>>>>

The hard problems (usually belongs to the NP-Complete category like 3-SAT) often require exponential computation time to traverse the solution space in a brute-force manner. In addition, people may need to solve the same types of problems again and again in different instances. Some instances or subproblems possibly have been solved by others. Therefore, we come to the idea that \emph{cache the existing solutions to those problems and query the solutions before we solve any other problems}.

One immediate challenge of this idea is the storage requirement. Even the same type of problem, e.g. 3-SAT, could have numerous problem instance, which may require several disks to store them, let alone we have many different types of hard problems. Cloud computing, at this point, could be a proper paradigm because it is much less expensive to build a large scale storage and its management system. The other challenge is how we abstract the hard problems in a way that the platform we build could be more general to many different types of hard problems.

In this document, we propose \emph{CloudCache} framework which is built on top of general cloud computing platform and provides the interface to query, cache and solve hard problems in an easier way. The CloudCache framework abstracts the \emph{problem-solution} pairs into \emph{key-value} objects, and uses some object storage system to cache existing problems and solutions. Further, the CloudCache framework provides a general problem solving interface \emph{kernel-solver}, so that the developer can easily write a problem's solution and solve it within the CloudCache's framework. CloudCache executes kernel-solver in a distributed way which tries to maximize the framework's problem solving throughput.

### 2013-05-04 paper/tex/performance.tex

\section{Evaluations} \label{sec:evaluation}
To evaluate the performance of the CloudCache and validate whether the cache idea is feasible in reality, we deploy the CloudCache framework to Amazon EC2 platform in a small scale (Fig.~\ref{fig:ec2}). In the deployment, there are $1$ Master Node, $4$ Slave Node/Data Node, and $1$ Sink Node. All EC2 instance are micro which have the specifications in Table~\ref{tab:ec2}.

@@

Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{tab:redis}. Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has $25316.46$ and $17421.60$ throughput respectively.

@@

Then we randomly generate $1,000,000$ 3-SAT problem instances, then the Client node submit those problem instances as a job to the Master Node. The Slave Node start solving the problem using kernel-solver and we collect the runtime statistics for the problem solving time and cache hit rate. Further, we use the Amazon CloudWatch as the system performance monitor tool to track the CPU usage and network consumption inside the framework.

@@

Second, we take a Slave Node's tracking results. As is shown in Fig.~\ref{fig:slave_cpu}, the Slave Node's CPU reaches to full load right after the job distribution phase of Master Node. During the next several hours, the Slave Node is busy solving problem assigned to itself. From Fig.~\ref{fig:slave_in} we can see the job receiving's in-network fringerprints. Once the Slave Node starts working, the out-network starts increase because the generated solutions will be sinked to the Sink Node. Thus, as is illustrated in Fig.~\ref{fig:slave_out}, the out-network starts busy right after the Slave Node starts working. Besides, the trends to grow in out-network indicates the problem solving throughput increases and it takes less and less time to solve a problem when we cache more and more solutions. However, the grows are sub-linear as $O(log^n)$ where $n$ is the number solutions cached. A possible reason is the EC2 instance type become a bottleneck for this framework.

Finally, the Sinker Node's CPU (Fig.~\ref{fig:sinker_cpu}) is in mild load because we adopt the solution report buffer in the Slave Node. The in-network (Fig.~\ref{fig:sinker_in}) confirms the conclusions that the framework is speeding up the problem solution as a whole, because the increase in the in-network has the same grow style with Slave Node's out-network. The Sinker Node's out-network (Fig.~\ref{fig:sinker_out}) also shows the ACKs for receiving data from TCP which has the similar shape with the in-network.

>>>>

\section{Evaluations} \label{sec:evaluation}
To evaluate the performance of the CloudCache and validate whether the cache idea is feasible in reality, we deploy the CloudCache framework to Amazon EC2 platform in a small scale (Fig.~\ref{fig:ec2}). In the deployment, there are $1$ Master Node, $4$ Slave Node/Data Node, and $1$ Sinker Node. All EC2 instances are micro which have the specifications in Table~\ref{tab:ec2}.

@@

Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{tab:redis}. Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has the throughput of $25316.46$ and $17421.60$ requests per second respectively.

@@

Then we randomly generate $1,000,000$ 3-SAT problem instances, then the Client node submit those problem instances as a job to the Master Node. The Slave Node starts solving the problem using kernel-solver and we collect the runtime statistics for the problem solving time and cache hit rate. Further, we use the Amazon CloudWatch as the system performance monitor tool to track the CPU usage and network consumption inside the framework.

@@

Second, we take a Slave Node's tracking results. As is shown in Fig.~\ref{fig:slave_cpu}, the Slave Node's CPU reaches to full load right after the job distribution phase of Master Node. During the next several hours, the Slave Node is busy solving problem assigned to itself. From Fig.~\ref{fig:slave_in} we can see the job receiving phase's in-network fringerprints. Once the Slave Node starts working, the out-network starts increasing because the generated solutions will be sinked to the Sinker Node. Thus, as is illustrated in Fig.~\ref{fig:slave_out}, the out-network starts busy right after the Slave Node starts working. Besides, the trends to grow in out-network indicates the problem solving throughput increases and it takes less and less time to solve a problem when we cache more and more solutions. However, the grows are sub-linear as $O(log^n)$ where $n$ is the number solutions cached. A possible reason is the EC2 instance type become a bottleneck for this framework.

Finally, the Sinker Node's CPU (Fig.~\ref{fig:sinker_cpu}) is in mild load because we adopt the solution report buffer in the Slave Node. The in-network (Fig.~\ref{fig:sinker_in}) confirms the conclusions that the framework is speeding up the problem solution as a whole, because the increase in the in-network has the same growing style with Slave Node's out-network. The Sinker Node's out-network (Fig.~\ref{fig:sinker_out}) also shows the ACKs for receiving data from TCP which has the similar shape to the in-network.
